---
title: "Improving Accessibility in Quarto Documents:"
subtitle: "Application to U.S. Stock Assessment Reports"
engine: lualatex
author:
  - name: "Samantha Schiano"
    affiliations:
    - name: "ECS Federal in Support of NOAA Fisheries OST"
      address: "2750 Prosperity Ave STE 600"
      city: "Fairfax"
      state: "VA"
      postal-code: '22031'
date: today
cover: partials/Petrale_sole.png
lang: en
keep-tex: true
format: 
  pdf: 
    documentclass: scrartcl
    number-sections: true
    template-partials:
      - 'partials/before-body.tex'
      - 'partials/_titlepage.tex'
    include-in-header:
      - 'partials/in-header.tex'
    toc: true
    lof: true
    lot: true
    titlepage-geometry: 
      - top=2in
      - bottom=1in
      - right=1in
      - left=1in
params:
   office: "NWFSC"
   species: "Petrale sole"
   spp_latin: "Eopsetta jordani"
bibliography:
  - references.bib
---

```{r}
#| label: "model_output"
#| echo: false 
#| warning: false 
#| eval: true 
output <- read.csv(file.path("data", "petrale_convert_output.csv")) |>
  dplyr::mutate(estimate = as.numeric(estimate))
# quantities
sb_ref <- output$estimate[grepl("spr_msy", output$label)][1]
f_ref <- output$estimate[grepl("f_msy", output$label)]
str_yr <- min(as.numeric(output$year[output$year!="S/Rcurve" | output$year!="Virg" | output$year!="Init"]), na.rm = TRUE)
end_yr <-  2023
  # max(as.numeric(output$year[output$year!="S/Rcurve" | output$year!="Virg" | output$year!="Init"]), na.rm = TRUE)
```

<!---
might need to add number-sections: true in yml
--->

{{< pagebreak >}}

**This content is only intended for use as a reproducible example to explore the ability to add accessibility features into a document generated by quarto. This document is not a scientific product and is not official communication of the National Oceanic and Atmospheric Administration, or the United States Department of Commerce**

{{< pagebreak >}}

## Introduction {#sec-intro}

The earliest catches of `r params$species` are reported in 1876 in California and 1884 in Oregon. `r params$species` were lightly exploited during the early 1900s, but new gear technology in the 1930s allowed trawling on new grounds and the fishery expanded to greater depths and to Oregon and Washington waters, resulting in larger landings. The `r params$species` catches further increased during World War II in response to increased demands. Also, during the “vitamin A rush” in the late 1930s and 1940s it was found that `r params$species` has high levels, which contributed to increased catches of this species as well. By the 1950s, the fishery was well developed with the stock showing declines in biomass and catches (Figures i and ii). Also in the 1950s, winter spawning grounds at deeper depths with dense concentrations of `r params$species` were discovered, and catches increased accordingly. The rate of decline in spawning biomass accelerated through the 1970s reaching minimums estimated to be generally around or below 10% of the unexploited levels during the 1980s through the early 2000s (Figure iii). Recent annual catches between 1981–2022 range between 803 and 3060 mt per year and the most recent landings are shown in Table i. `r params$species` are a desirable market species and discarding has historically been low (less than 5.1%), with most of the discarding due to small sizes.

There is little information regarding the stock structure of `r params$species` off the U.S. West Coast. No genetic research has been undertaken for `r params$species` and there is no other published research indicating separate stocks of `r params$species` within U.S. waters. Tagging studies show adult `r params$species` can move as much as 500 km, having the ability to be highly migratory with the possibility for homing ability [@alverson_results_1957]. Juveniles show little coastwide or bathymetric movement while studies suggest that adults generally move inshore and northward onto the continental shelf during the spring and summer to feeding grounds and offshore and southward during the fall and winter to deep water spawning grounds [@horton_species_1989; @love_milton_probably_1996]. Adult `r params$species` can tolerate a wide range of bottom temperatures [@perry_environmental_1994].

The `r params$office` has updated the assessment for `r params$species` along the U.S. West Coast to help identify any concerns for management and aid in management decisions. 

## Data {#sec-data}

Data comprise the foundational components of stock assessment models.
The decision to include or exclude particular data sources in an assessment model depends on many factors.
These factors often include, but are not limited to,
the way in which data were collected (e.g., measurement method and consistency);
the spatial and temporal coverage of the data;
the quantity of data available per desired sampling unit;
the representativeness of the data to inform the modeled processes of importance;
timing of when the data were provided;
limitations imposed by the Terms of Reference; and
the presence of an avenue for the inclusion of the data in the assessment model. 
Attributes associated with a data source can change through time,
as can the applicability of the data source when different modeling approaches are explored (e.g., stock structure or time-varying processes).
Therefore, the specific data sources included or excluded from this assessment should not necessarily constrain the selection of data sources applicable to future stock assessments for `r params$species`.
Even if a data source is not directly used in the stock assessment they can provide valuable insights into biology, fishery behavior, or localized dynamics.Data comprise the foundational components of stock assessment models.
The decision to include or exclude particular data sources in an assessment model depends on many factors.
These factors often include, but are not limited to,
the way in which data were collected (e.g., measurement method and consistency);
the spatial and temporal coverage of the data;
the quantity of data available per desired sampling unit;
the representativeness of the data to inform the modeled processes of importance;
timing of when the data were provided;
limitations imposed by the Terms of Reference; and
the presence of an avenue for the inclusion of the data in the assessment model. Included is a reference to @sec-intro.
Attributes associated with a data source can change through time,
as can the applicability of the data source when different modeling approaches are explored (e.g., stock structure or time-varying processes).
Therefore, the specific data sources included or excluded from this assessment should not necessarily constrain the selection of data sources applicable to future stock assessments for `r params$species`.
Even if a data source is not directly used in the stock assessment they can provide valuable insights into biology, fishery behavior, or localized dynamics.

Since 2011, trawl fisheries have been managed with catch shares under a system of annual individual fishing quotas (IFQs) for the shoreside sector (i.e., vessels delivering to shoreside processors) and harvest cooperatives for the at-sea hake sectors (catcher-processors who catch and process hake at sea; and Motherships, factory processors that take delivery of hake from catcher vessels at sea). Constant monitoring of catch using observers or electronic monitoring (EM) is required to participate in the trawl catch share fishery.

## Results {#sec-results}

The model fits the (s-wcgbt) index very well, including a decline from 2005 to 2009 followed by a rapid increase to a plateau in 2013--2017 and a gradual decline to the most recent observations (@fig-spawn_bio). The observations that fit the least well are 2018 and 2019, which were lower than the years before and after. The absence of a 2020 survey due to the COVID-19 pandemic makes it difficult to determine if those two years were just outliers or if there was some unexplained population dynamics leading to a reduction in available biomass for those years.

When an extra standard deviation parameter was estimated for the (s-wcgbt), the value was minimal, indicating that the index fits well enough to not require additional tuning. These findings can have major implications to management (See @sec-discussion).

The terminal year (`r end_yr`) spawning biomass reference point was valued at `r sb_ref` when fishing was occurring at `r f_ref`. This changed drastically over the period of `r end_yr - str_yr` years (management and monitoring beginning in `r str_yr`).

## Discussion {#sec-discussion}

## Impact to Management {#sec-impact}

Improve him believe opinion offered met and end cheered forbade. Friendly as stronger speedily by recurred. Son interest wandered sir addition end say. Manners beloved affixed picture men ask. Explain few led parties attacks picture company. On sure fine kept walk am in it. Resolved to in believed desirous unpacked weddings together. Nor off for enjoyed cousins herself. Little our played lively she adieus far sussex. Do theirs others merely at temper it nearer.

Received overcame oh sensible so at an. Formed do change merely to county it. Am separate contempt domestic to to oh. On relation my so addition branched. Put hearing cottage she norland letters equally prepare too. Replied exposed savings he no viewing as up. Soon body add him hill. No father living really people estate if. Mistake do produce beloved demesne if am pursuit.

Affronting discretion as do is announcing. Now months esteem oppose nearer enable too six. She numerous unlocked you perceive speedily. Affixed offence spirits or ye of offices between. Real on shot it were four an as. Absolute bachelor rendered six nay you juvenile. Vanity entire an chatty to.

### Considerations {#sec-considerations}

That know ask case sex ham dear her spot. Weddings followed the all marianne nor whatever settling. Perhaps six prudent several her had offence. Did had way law dinner square tastes [@haltuch2019sable]. Recommend concealed yet her procuring see consulted depending. Adieus hunted end plenty are his she afraid. Resources agreement contained propriety applauded neglected use yet.

Months on ye at by esteem desire warmth former. Sure that that way gave any fond now. His boy middleton sir nor engrossed affection excellent [@wetzel2019petrale]. Dissimilar compliment cultivated preference eat sufficient may. Well next door soon we mr he four. Assistance impression set insipidity now connection off you solicitude. Under as seems we me stuff those style at. Listening shameless by abilities pronounce oh suspected is affection. Next it draw in draw much bred.


## References

::: {#refs} 
:::


## Figures

```{r, fig.cap = paste("This is a great caption explaining a trend of spawning biomass of", params$species, "in", end_yr, " test in-line code", f_ref, ".")} 
#| label: 'fig-spawn_bio'
#| echo: false 
#| warning: false 
#| eval: true 
#| fig-alt: 'this describes the trend.'
satf::plot_spawning_biomass(dat = output, ref_line = 'target', end_year = end_yr)
``` 
